---
title: "R basics"
author: "Jiho Yeo"
date: '2021 3 3 '
output: html_document
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The very basics

### Objects

We use `<-` to assign values to the variables (objects).

```{r}
a <- 1 
a = 1

a
print(a)
```

### The workspace

```{r}
ls()
```

```{r}
b <- 1
c <- -1

# 판별식
d <- (-b + sqrt(b^2 - 4*a*c) ) / ( 2*a )  #sqrt:제곱근
d
```
### Functions

- R에서 기본적으로 제공하는 함수들이 존재  
- 특정 패키지를 다운받는다면 해당 팩키지에서 정의한 함수 사용 가능  
- 본인이 직접 함수를 만들 수 있음: `function`


```{r}
# 도움말 열기
?rep

#google: r rep / r rep example / r rep 예제

#rep:일정한 데이터 반복

# Basic
rep(3,5)

# times
rep(c(1,2,3),times=5)

# each
rep(c(1,2,3),times=5, each=2)
```

```{r}
# 도움말 열기
?seq 
#seq() : 일정한 구조/순차 데이터 생성

seq(from=1,to=10)
seq(1,10)
1:10

# by
seq(1,10, by=2)

# length.out
seq(1,10, length.out=3)

```

## Data type

### Vector

We can create vectors using the function `c`, which stands for concatenate.

```{r}
codes <- c(380, 124, 818)

codes
```

We can also create character vectors. We use the quotes to denote that the entries are characters rather than variable names.

```{r}
country <- c("italy", "canada", "egypt")

country <- c(italy, canada, egypt)

italy <- 1
canada <- 2
egypt <- 3

country <- c(italy, canada, egypt)
country
```

### Subsetting

We use square brackets to access specific elements of a vector.

```{r}
codes

codes[2]
```

You can get more than one entry by using a multi-entry vector as an index:

```{r}
codes[c(1,3)]
```

The sequences defined above are particularly useful if the length of the vector is long

```{r}
#1~1000까지 5씩 차이나게 불러오기
codes <- seq(1,1000,5)
codes

#100까지 추출 (5씩 차이나게)
codes[1:100]
```

### Data frames 

```{r}
#install.packages("dslabs")
library(dslabs)

data(murders)

class(murders)
```

### Examning an object 

The function `str` is useful for finding out more about the structure of an object:

```{r}

#해당 변수의 속성과 길이, 그리고 미리보기 값을 제공합니다.
?str
str(murders)
```

This tells us much more about the object. We see that the table has 51 rows (50 states plus DC) and five variables. We can show the first six lines using the function `head`:

```{r}
#처음 6개 행 보여주는 함수
head(murders)
```

### The accessor: `$`

We will need to access the different variables represented by columns  
To do this, we use the accessor operator `$` in the following way:
열로 표시된 여러 변수에 액세스해야 합니다.
이를 위해 다음 방법으로 접근자 연산자 '$'를 사용한다.
```{r}
murders$population
```

### Vectors: numerics, characters, and logical

```{r}
pop <- murders$population
# 벡터의 길이, dataframe의 열의 개수를 셀 때 사용하는 함수입니다.
length(pop)   

class(pop)
```

```{r}
class(murders$state)
```

Another important type of vectors are logical vectors. These must be either `TRUE` or `FALSE`

```{r}
3 == 2
z <- (3==2)
z

class(z)

?Comparison
```


### Factor

In the `murders` dataset, we might expect the region to also be a character vector. However, it is not:

```{r}
class(murders$region)
```

It is a factor. Factors are useful for storing categorical data. We can see that there are only 4 regions by using the `levels` function:
그것은 factor이다. factor은 범주형 데이터를 저장하는 데 유용합니다. '레벨' 기능을 사용하면 4개 지역만 있음을 알 수 있다.

```{r}
levels(murders$region)
```

In the background, R stores these levels as integers and keeps a map to keep track of the labels. This is more memory efficient than storing all the characters.

```{r}
murders$region
```

### Lists

Data frames are a special case of lists. Lists are useful because you can store any combination of different types. You can create a list using the `list` function like this:

```{r}
record <- list(name = "John Doe",
               student_id = 1234,
               grades = c(95, 82, 91, 97, 93),
               final_grade = "A")

record
```

```{r}
record$grades
```

### Matrix

```{r}
mat <- matrix(1:12, 4, 3)

mat
```

Matrix Indexing

```{r}
mat[2, 3]

mat[2, ]

mat[, 3]

mat[, 2:3]

mat[1:2, 2:3]
```

Convert matrix to dataframe

```{r}
as.data.frame(mat)
```


